Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
Case description review

\section{Case Company Description} \label{case_company_description}
The case company is a company operating in the domain of video surveillance. The company has its headquarters in Lund, Sweden with offices in 49 countries worldwide. The company is the global market leader in the markets of network cameras and video encoders. The develops embedded software for the security cameras. The cameras are designed to be accessible through APIs that are developed and maintained by the company.

The API analysed in this study has been deployed for several years. It was recently updated from version 1.4 to version 2.0, which is the current active version. The changes between these two versions is what has been analysed in this study. Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms. The API is used by company partners, which are companies who develop applications for the cameras. These applications are, in turn, used by the end-users of the cameras. The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.

>>>>

\section{Case Company Description} \label{case_company_description}
The case company is a company operating in the domain of video surveillance. The company has its headquarters located in Lund, Sweden, with offices in 49 countries worldwide. The company is the global market leader in the markets of network cameras and video encoders. They develop embedded software for security cameras. The cameras are designed to be accessible through APIs that are developed and maintained by the company.

The API analysed in this study has been deployed for several years. It was recently updated from version 1.4 to version 2.0, which is the current active version. The changes between these two versions is what has been analysed in this study. Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms (``Bit odd the end of this sentence'')(``version 1.0 to 1.4 only included additional build options and did not include the addition of new functionality''). The API is used by company partners, which are companies who develop applications for the cameras. These applications are, in turn, used by the end-users of the cameras. The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.
